---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidykids

<!-- badges: start -->
<!-- badges: end -->

The not-for-profit organization the [Urban Institute](https://www.urban.org/) created an incredible dataset on State-by-State Spending on Kids that is available [here](https://datacatalog.urban.org/dataset/state-state-spending-kids-dataset). 

This data package provides this dataset through R. It is formatted as [tidy data](https://vita.had.co.nz/papers/tidy-data.pdf) to facilitate analysis within the [tidyverse](https://www.tidyverse.org/) suite of R packages.

The data was made available by and is attributable to Julia Isaacs, Eleanor Lauderback, and Erica Greenberg under the under the ODC Attribution License (https://opendatacommons.org/licenses/by/1-0/).

## Installation

You can install {tidykids} only from GitHub with:

``` r
remotes::install_github("jrosen48/tidykids")
```

## Use

First, load the {tidykids} package:

```{r example}
library(tidykids)
```

Then, type `tidykids` to load the data:

```{r}
tidykids
```

To see descriptions of the variables (also available [here](https://datacatalog.urban.org/sites/default/files/data-dictionary-files/State-by-State%20Spending%20on%20Kids%20Data%20Dictionary%20File_0.xlsx)):

```{r}
tidykids_data_dictionary
```

These are also presented in an easily-readable format in the [tidykids-codebook vignette](tidykids-codebook.html).
