---
title: "tidykids-codebook"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidykids-codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

- `state` refers to the United States state (including the District of Columbia)
- `year` refers to the year
- `raw` refers to the raw amount spent
- `inf_adj` refers to the amount transformed to be in 2016 dollars for each year spent
- `inf_adj_per_child` refers to the amount transformed to be in 2016 dollars for each year per child

**Note that the descriptions are for the `raw` amount spent; `int_adj` and `int_adj_per_child` are based upon that amount.**

```{r, echo = FALSE, message = FALSE}
library(DT)
library(readr)
library(dplyr)
tidykids_data_dictionary <- read_csv('tidykids_data_dictionary.csv')
tidykids_data_dictionary <- tidykids_data_dictionary %>% rename(Expenditure = `Variable name`)
datatable(tidykids_data_dictionary, options = list(pageLength = 30))
```
